---
title: "Who does more pushups"
author: "your name"
date: "March 8"
output: html_document
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(tigerstats)
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

Several years ago some MAT 111 students who were on the footbal team conducted a study of their team-mates.  The results are contained in the data frame `pushups` in the `tigerstats` package.

```{r eval=FALSE}
data(pushups)
View(pushups)
help(pushups)
```

Among other things, the students recorded the type of position a player had on the team (either line or skill), and also the number of push-ups each player could perform in a two-minute period.

Line players are on the offensive or defensive line.  They need to be a certain kind of speed, but they must also be quite big and strong.  Skill players do a lot of runninga and catching:  they are the quarterback, running backs, receivers, etc.

Our Research Question is:

  >Who does more pushups, on average: a line player or a skill player?


# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->






# Results
<!--You have both graphical and numerical methods, so you will have both graphical and numerical results to consider.!-->


## Graphical Results
<!--Your graph should have a good title, and axes should be labled as needed.  Discuss your graphical results, showing how they answer the research question.  Use specific features of the graph in your discussion.!-->


## Numerical Results
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


# Inferential Results
<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion
<!--State your overall conclusion.  This is also a good place to mention other Research Questions that came to mind as you were carrying out this study.!-->
  
By exploring all the methods used in this report (box and whisker plot, variable analysis, t-test and observing the p-value), we can logically conclude that skill players do more pushups than line players. The box and whisker plot visually showed the significant differences of the data within the two groups, the variable analysis showed the exact numbers from which we were able to conclude that the skill players' average of pushups done was way higher than the average of the line players', and the t-test & p-value inferences allowed us to favor the alternate hypothesis, which stated that there clearly IS a relationship between the position a player plays on a football team and the amount of pushups they can do. Should this study be done again on a different football team, the results would be similar.   
Other research questions that could potentially come from this study include:  
- In terms of weight, can heavier players do more pushups than lighter players?   
- Can heavier skill players do more pushups than lighter skill players? 
